A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-21 paper/paper.Rnw
Clean out more comments

The first rows of \autoref{fig:exemplars} are images which contain only one of the nine classes. Most of the predictions for these images are promising; there are some false-positive labels that indicate confusions between circle/text and polygon/quad, but all of the true shapes are corectly identified by the model above EER. The next image belongs to the ``other" category, as it does not contain any of the nine classes; the model correctly assigns near-zero probabilities to each class. The final rows are of images that belong to more than one class category. Again, predictions are largely accurate, with most of the prominent shapes correctly identified above EER. \fix{These are mostly new examples from our last meeting because many of the previous images were in the training set... Grrrrr..... I have two or three too many, not sure about color contrast within images, etc., feel free to delete a few or we can discuss them. [Expand on specific misclassifications more, after determining which examples to delete.]}

@@

While figure \ref{fig:exemplars} shows representative examples of classifications across multiple shape categories, it is also useful to examine many cases within a given shape to get a sense of model consistency. \autoref{fig:circle-text-consistency} shows a number of images containing circles and/or text. \fix{this isn't accurate to what I'm seeing...} \fix{The top four rows show text contained within a separate, distinct circle shape, and the next five rows show circles represented as the letter ``o" in text. The remaining images contain only one of either text or circles, as well as other possible shape categories.} In particular, the first two of these images contain text that use the capital letter ``G", the next two images contain no circular shapes, and the final \fix{N} images contain pure circles that do not appear to belong to text. The model is able to identify the circle in all cases where a circle is truly present, regardless of whether the circle is part of the text or it is distinct; however, the circle prediction is also strong in three of the four images that do not contain a circle, which indicates that the model is having dificulty distinguishing the two categories. \svp{While the circle predictions are above the EER for letters such as C and S, these predictions are generally much lower than those where distinct circles or Os are seen, indicating that there are some indications that features are not as strong in the quasi-circle shapes, but that the model is not able to completely separate Os from C, S, and G shapes which are also very circular.} This confusion is complicated by the frequency of images which contain both circles and text: text is present in \Sexpr{100 * round(sum(as.logical(grepl("circle", dfunion$name) & grepl("text", dfunion$name))) / sum(grepl("circle", dfunion$name)), 2)}\% of our labeled images containing circles, and circles are present in \Sexpr{100 * round(sum(as.logical(grepl("circle", dfunion$name) & grepl("text", dfunion$name))) / sum(grepl("text", dfunion$name)), 2)}\% of our images containing text. In addition, the distinction between a circle and an ``o" comes from the context around the shape, which is much more difficult for the model to parse than simply detecting a shape. More importantly, this behavior does not suggest poor model performance as much as a weakness of the classification scheme, which will be discussed in a later section.

@@

\paragraph{Confusion Matrix}
Figures \ref{fig:exemplars} and \ref{fig:circle-text-consistency} show predictions for a number of individual images. Many of the misclassifications in these examples, however, are not just seen in individual images, but rather exist systematically between certain classes. % Nicely phrased!!! I couldn't have done it better myself.
A confusion matrix is a type of visualization that summarizes the relationships between the labels assigned to an image and the labels predicted by the model across all test data, and is a helpful diagnostic tool to understand which classes are systematically misclassified. The confusion matrix for the fitted model is presented in \autoref{fig:confusion-matrix}. %mt{Each value in the matrix represents the probability of assigning the label associated with that value's corresponding row, conditional upon the image truly belonging to the category associated with the value's column. Thus, }
The values along the diagonal of the matrix represent the proportion of true positives captured within each category. The off-diagonal values represent the proportion of false positives for each shape pairing; however, since a single image may truly contain multiple shapes, the values have been adjusted to remove the effect of any true positives from the calculation of false positive proportions. Thus, this might be considered a conditional confusion matrix, because we condition the off diagonal probabilities on the label not being correct. For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any images that truly contains both triangles and quadrilaterals are removed before calculating the proportion of false quadrilateral labels. As a result of this adjustment, the off-diagonal values of the confusion matrix are the proportion of images within a true class (column-wise) that are falsely labeled as containing another class that has not been labeled in the image (row-wise). Note that this matrix is not symmetric: the proportion of images containing text that are falsely predicted to contain circles is not necessarily equal to the proportion of images containing circles that are falsely predicted to contain text.

@@

%The confusion between text and circles is a natural consequence of the overlap between geometric shapes and components of written text; it is not indicative of a lack of fit as much as a weakness in the classification system used to define the model.

\paragraph{Feature Overlap}
%\paragraph{Brand Investigations}
We have defined our categories through consultation with practitioners and modifications of previous research, but as a result, there are a number of features (such as lines, angles, and curves) which are not unique to only one category. For example:
\begin{itemize}
\item a triangle may be made up of three acute angles, but a quad can also contain three acute angles.
\item the only distinction between an ``o" and a circle is whether there is more text around it.
\item the only difference between lines and thin repeating quads are the ends of the shapes.
\end{itemize}

@@

% \mt{Note to self: I feel like I want the heatmaps concentrated in one spot, and it would feel like a strange interjection to explain them earlier. However, I mostly see including them as a way to support the claims we've been making throughout the paper, so I could definitely imagine an argument for including them earlier for specific examples so that saying ``the model sees..." is less speculatory...}

>>>>

The first rows of \autoref{fig:exemplars} are images which contain only one of the nine classes. Most of the predictions for these images are promising; there are some false-positive labels that indicate confusions between circle/text and polygon/quad, but all of the true shapes are corectly identified by the model above EER. The next image belongs to the ``other" category, as it does not contain any of the nine classes; the model correctly assigns near-zero probabilities to each class. The final rows are of images that belong to more than one class category. Again, predictions are largely accurate, with most of the prominent shapes correctly identified above EER. \fix{Expand on specific misclassifications more, after determining which examples to delete.}

@@

While figure \ref{fig:exemplars} shows representative examples of classifications across multiple shape categories, it is also useful to examine many cases within a given shape to get a sense of model consistency. \autoref{fig:circle-text-consistency} shows a number of images containing circles and/or text. \fix{The top four rows show text contained within a separate, distinct circle shape, and the next five rows show circles represented as the letter ``o" in text. The remaining images contain only one of either text or circles, as well as other possible shape categories.} In particular, the first two of these images contain text that use the capital letter ``G", the next two images contain no circular shapes, and the final \fix{N} images contain pure circles that do not appear to belong to text. The model is able to identify the circle in all cases where a circle is truly present, regardless of whether the circle is part of the text or it is distinct; however, the circle prediction is also strong in three of the four images that do not contain a circle, which indicates that the model is having dificulty distinguishing the two categories. While the circle predictions are above the EER for letters such as C and S, these predictions are generally much lower than those where distinct circles or Os are seen, indicating that there are some indications that features are not as strong in the quasi-circle shapes, but that the model is not able to completely separate Os from C, S, and G shapes which are also very circular. This confusion is complicated by the frequency of images which contain both circles and text: text is present in \Sexpr{100 * round(sum(as.logical(grepl("circle", dfunion$name) & grepl("text", dfunion$name))) / sum(grepl("circle", dfunion$name)), 2)}\% of our labeled images containing circles, and circles are present in \Sexpr{100 * round(sum(as.logical(grepl("circle", dfunion$name) & grepl("text", dfunion$name))) / sum(grepl("text", dfunion$name)), 2)}\% of our images containing text. In addition, the distinction between a circle and an ``o" comes from the context around the shape, which is much more difficult for the model to parse than simply detecting a shape. More importantly, this behavior does not suggest poor model performance as much as a weakness of the classification scheme, which will be discussed in a later section.

@@

\paragraph{Confusion Matrix}
Figures \ref{fig:exemplars} and \ref{fig:circle-text-consistency} show predictions for a number of individual images. Many of the misclassifications in these examples, however, are not just seen in individual images, but rather exist systematically between certain classes. A confusion matrix is a type of visualization that summarizes the relationships between the labels assigned to an image and the labels predicted by the model across all test data, and is a helpful diagnostic tool to understand which classes are systematically misclassified. The confusion matrix for the fitted model is presented in \autoref{fig:confusion-matrix}. The values along the diagonal of the matrix represent the proportion of true positives captured within each category. The off-diagonal values represent the proportion of false positives for each shape pairing; however, since a single image may truly contain multiple shapes, the values have been adjusted to remove the effect of any true positives from the calculation of false positive proportions. Thus, this might be considered a conditional confusion matrix, because we condition the off diagonal probabilities on the label not being correct. For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any images that truly contains both triangles and quadrilaterals are removed before calculating the proportion of false quadrilateral labels. As a result of this adjustment, the off-diagonal values of the confusion matrix are the proportion of images within a true class (column-wise) that are falsely labeled as containing another class that has not been labeled in the image (row-wise). Note that this matrix is not symmetric: the proportion of images containing text that are falsely predicted to contain circles is not necessarily equal to the proportion of images containing circles that are falsely predicted to contain text.

@@

\paragraph{Feature Overlap}
We have defined our categories through consultation with practitioners and modifications of previous research, but as a result, there are a number of features (such as lines, angles, and curves) which are not unique to only one category. For example:
\begin{itemize}
\item a triangle may be made up of three acute angles, but a quadrilateral can also contain three acute angles.
\item the only distinction between an ``o" and a circle is whether there is more text around it.
\item the only difference between lines and thin repeating quads are the ends of the shapes.
\end{itemize}

@@
